### 2021-02-21 newvariant.tex
fix
moving caption

\begin{itemize}
  \item People want to estimate strength of new variant from speed
  \item Typically assume same GI distribution
  \item Recent evidence that GI of the new variant might be longer
  \item How does that affect our estimates?
\end{itemize}

@@

\begin{figure}[!th]
\includegraphics[width=\textwidth]{relstrength.pdf}
\caption{
\textbf{Relative strength of the new variant given observed relative speed.}
}
(A) True relative strength of the new variant $\theta$ given speed of the wild type $r_w$ and the relative speed $\delta$.
The dashed contour line corresponds to $\theta = 1$.
True relative strength of the new variant $\theta$ is calculated using $\bar{G}_w = 5\,\textrm{days}$, $\bar{G}_v = 8\,\textrm{days}$, and $\kappa = 1/5$. 
(B) Estimated relative strength of the new variant $\hat{\theta}$ given speed of the wild type
$r_w$ and the relative speed $\delta$ assuming identical generation-interval distributions.
(C) Biases in the estimates of the relative strength of the new variant $\hat{\theta} - \theta$ given speed of the wild type $r_w$ and the relative speed $\delta$.
The dashed contour line corresponds to $\hat{\theta} = \theta$.
\label{fig:relstrength}
\end{figure}

@@

\begin{figure}[!th]
\includegraphics[width=\textwidth]{relspeed.pdf}
\caption{
\textbf{Relative speed of the new variant given assumed relative strength.}
}
(A) True relative speed of the new variant $\delta$ given strength of the wild type $\RR_w$ and the relative strength $\theta$.
The dashed contour line corresponds to $\delta = 0$.
True relative speed of the new variant $\delta$ is calculated using $\bar{G}_w = 5\,\textrm{days}$, $\bar{G}_v = 8\,\textrm{days}$, and $\kappa = 1/5$. 
(B) Estimated relative speed of the new variant $\hat{\delta}$ given strength of the wild type $\RR_w$ and the relative strength $\theta$ assuming identical generation-interval distributions.
(C) Biases in the estimates of the relative speed of the new variant $\hat{\delta} - \delta$ given strength of the wild type $\RR_w$ and the relative strength $\theta$.
The dashed contour line corresponds to $\hat{\delta} = \delta$.
\label{fig:relspeed}
\end{figure}

>>>>

@@

\begin{figure}[!th]
\includegraphics[width=\textwidth]{relstrength.pdf}
\caption{
\textbf{Relative strength of the new variant given observed relative speed.}
(A) True relative strength of the new variant $\theta$ given speed of the wild type $r_w$ and the relative speed $\delta$.
The dashed contour line corresponds to $\theta = 1$.
True relative strength of the new variant $\theta$ is calculated using $\bar{G}_w = 5\,\textrm{days}$, $\bar{G}_v = 8\,\textrm{days}$, and $\kappa = 1/5$. 
(B) Estimated relative strength of the new variant $\hat{\theta}$ given speed of the wild type
$r_w$ and the relative speed $\delta$ assuming identical generation-interval distributions.
(C) Biases in the estimates of the relative strength of the new variant $\hat{\theta} - \theta$ given speed of the wild type $r_w$ and the relative speed $\delta$.
The dashed contour line corresponds to $\hat{\theta} = \theta$.
}
\label{fig:relstrength}
\end{figure}

@@

\begin{figure}[!th]
\includegraphics[width=\textwidth]{relspeed.pdf}
\caption{
\textbf{Relative speed of the new variant given assumed relative strength.}
(A) True relative speed of the new variant $\delta$ given strength of the wild type $\RR_w$ and the relative strength $\theta$.
The dashed contour line corresponds to $\delta = 0$.
True relative speed of the new variant $\delta$ is calculated using $\bar{G}_w = 5\,\textrm{days}$, $\bar{G}_v = 8\,\textrm{days}$, and $\kappa = 1/5$. 
(B) Estimated relative speed of the new variant $\hat{\delta}$ given strength of the wild type $\RR_w$ and the relative strength $\theta$ assuming identical generation-interval distributions.
(C) Biases in the estimates of the relative speed of the new variant $\hat{\delta} - \delta$ given strength of the wild type $\RR_w$ and the relative strength $\theta$.
The dashed contour line corresponds to $\hat{\delta} = \delta$.
}
\label{fig:relspeed}
\end{figure}
